On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-31 paper/paper.tex
Removed a widow
wibble
Making the abstract one paragraph
Note the removal of the word traditional (for spacing only).

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
% Say what problem is
  Capturing control flow is the Achilles heel of Haskell-based
  deeply embedded domain specific languages.
  Rather than use
  the builtin control flow mechanisms, artificial control flow combinators
  are used instead.

% Say why it is an interesting problem
  However, capturing traditional control flow in an deeply embedded domain specific language
  would support the writing of programs in a natural style by allowing the programmer to use the
  constructs that are already builtin to the base language, such as pattern
  matching and recursion.
% Say what our solution achieves

  In this paper, we expand the capabilities of traditional,
  Haskell-based, deep embeddings with a compiler extension
  for reifying conditionals and pattern matching.
% Here is why the world will be a better place
  With this new support, the Haskell that we capture for expressing
  deeply embedded domain specific languages can be cleaner, Haskell-idiomatic,
  and more declarative in nature.

@@

  construct :: t -> E (ERepTy t)

  rep :: t -> E t

@@

  unrep' :: ERepTy t -> t

  rep' :: t -> ERepTy t
\end{lstlisting}

@@

  rep (Left x)  = LeftExp (rep x)
  rep (Right y) = RightExp (rep y)

  unrep' = id
  rep'   = id

@@

\break

@@

A C code generation function \ttt{genC} is implemented

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
% Say what problem is
  Capturing control flow is the Achilles heel of Haskell-based
  deeply embedded domain specific languages.
  Rather than use
  the builtin control flow mechanisms, artificial control flow combinators
  are used instead.
% Say why it is an interesting problem
  However, capturing traditional control flow in an deeply embedded domain specific language
  would support the writing of programs in a natural style by allowing the programmer to use the
  constructs that are already builtin to the base language, such as pattern
  matching and recursion.
% Say what our solution achieves
  In this paper, we expand the capabilities of
  Haskell-based deep embeddings with a compiler extension
  for reifying conditionals and pattern matching.
% Here is why the world will be a better place
  With this new support, the Haskell that we capture for expressing
  deeply embedded domain specific languages can be cleaner, Haskell-idiomatic,
  and more declarative in nature.

@@

  construct :: t -> E (ERepTy t)
  rep :: t -> E t

@@

  unrep' :: ERepTy t -> t
  rep' :: t -> ERepTy t
\end{lstlisting}

@@

  rep (Left x)  = LeftExp (rep x)
  rep (Right y) = RightExp (rep y)
  unrep' = id
  rep'   = id

@@

% \break

@@

A C code generation function \ttt{genC} is implemented:
